\propertitle

### 2019-06-17 maxNt_v5.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-06-17T16:26:01+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal network\\ from subnetwork data%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

In the next section we apply this method to the data sets from two actual
recordings, and discuss the properties of the resulting distributions.

@@

The first data set, from \textcite[rat 14147]{stensolaetal2012}, consists
of $n=65$ neurons (27 of which classified as grid cells) from rat Medial
Entorhinal Cortex, recorded for about 20 minutes. Their spikes are
binned ainto $T=417\,641$ bins of $3\;\textrm{ms}$ width.

The second data set, from \textcite{rostamietal2016_r2017}, consists of
$n=159$ neurons from macaque Motor Cortex, recorded for about 15 minutes.
Their spikes are binned ainto $T=300\,394$ bins of $3\;\textrm{ms}$ width.

\texttt{data\_RS.npy}

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-06-17T17:13:33+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal network\\ from subnetwork data%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

The number of moments used with this method depends on the specific
questions and hypotheses that a researcher is exploring; for example,
hypotheses of sufficient statistics, such as the sufficiency of pairwise
correlations for inferential purposes. In the present work we only want to
present the general method without entering into biological questions of
this kind. The particular case in which $n$ moments are constrained
corresponds to fully specify the measured time-frequency distribution of
the sample activity. In this case, our inferences about the full-network
activity are using all available measured frequency data. Using the full
frequency distribution of the sample may be a bad idea, however, because
the maximum-entropy distribution becomes a bad approximation of some of the
four distributions described above. It is preferable to use a moderately
high number of moments smaller than $n$. We explain this point in \sect***.

In the next section we apply the method to the data sets from two actual
recordings, using *** moments, and discuss the properties of the resulting
distributions.

@@

The first data set, from \textcite[rat 14147]{stensolaetal2012}, consists
of $n=65$ neurons (27 of which classified as grid cells) from rat Medial
Entorhinal Cortex, recorded for about 20 minutes. Their spikes are
binned into $T=417\,641$ bins of $3\;\textrm{ms}$ width.

The second data set, from
\textcite{rostamietal2016_r2017}, %\texttt{data\_RS.npy}
consists of $n=159$ neurons from macaque Motor Cortex, recorded for about
15 minutes. Their spikes are binned into $T=300\,394$ bins of
$3\;\textrm{ms}$ width.
